\lettrine[lines=2]Spending nearly four years writing a thesis on bird song is undoubtedly one of the weirdest, most privileged things a human can do. And yet, somehow, it's still not easy: I couldn't have done it without the help of many people, so some thanks are in order.

Around five years ago, as I was completing my degree in Anthropology, I cold-emailed Ben, who would later become my supervisor: 'Hey, I'm interested in cultural change in bird song, can I come and record your birds?' (I'm paraphrasing, of course, it was more like 'Dear Professor Sheldon ...'), To my surprise, he generously provided me with a scientific home and the necessary infrastructure for my project. I'd like to think that he'd have second thoughts about that decision now that he knows me better. As a consequence, I've now learnt more than I ever wanted to know about phenology and breeding ecology in a lab that turned out to be made up of a bunch of kind and supportive people. This may or may not be a coincidence, given that Ben is a kind and supportive individual himself. So, thank you, Ben, for being a good scientist, mentor, and human. 

Ella Cole has been my co-supervisor, which I'm very thankful for. She has done, and still does, a very good job at providing scientific advice to students, and, perhaps most importantly, helping to create an atmosphere where people can discuss their woes and these are not just brushed off---because my oh my are we not all a bit broken. I already said that the people in the lab are nice, but seriously, they are. I am tremendously lucky to be able to call some of them my friends. To all of them, from the bottom of my heart: thanks for putting up with me these last few years. Even after only a few years as a lowly student, I have already had a glimpse of an academia that can be competitive, a tad nasty, and motivated by all the wrong reasons, but none of it I've seen within the current iteration of this group: everyone understands that the science is, as it should be, secondary.

Whatever I've learned about programming, statistics and bioacoustics - all new to me - I fully owe it to all the people who share their code, data, and expertise altruistically on the internet, so thank you, faceless and often thankless open source and open science community! I would have definitely been more productive if I hadn't spent so much time learning about packaging, reproducibility, and sustainability, but I choose to believe that time was not wasted.

And then there's Carys Jones, who went from another student that I would bump into in the woods to an indispensable part of life, and has made this time at Oxford---and, I hope, many times to come, here and elsewhere---much better, fun, and interesting. I am grateful beyond words for your friendship and patience, your help and support, all the good and bad times already spent together in the last few years. This thesis owes a lot to you, too.

I am extremely lucky to have the family I have. It has been a while since I left the nest myself (almost 12 years now!), but they are in everything I do---well, not in everything, just the good and reasonable bits. My parents, Olga and Nilo, taught me to love nature and nurtured my curiosity, allowed me to explore the world, and have always been exceptionally loving and non-judgemental. My brothers, David and Juan, are also wonderful individuals who have taught me a lot, and I'm immensely proud of them. I don't say this nearly often enough, and a PhD thesis is kind of a weird place to do so, but I love them all dearly. The rest of my family is pretty great too!

More than seven years ago, shortly after I quit my old job, and before I had gone to university, I found myself hitchhiking across the Balkans with Andrea. It was a lot of fun, but neither of us could have possibly imagined that we'd be finishing our PhDs together all these years later. (As a matter of fact she's helping me draft the conclusions as I write this, because, very psychosomatically in character for me, I got shingles on my face and a headache like a hammer.) Back then I was debating whether it was worth going to uni at all, concluded 'well I got some savings, what can I lose' [narrator: he lost all of his hard-earned savings] and moved to the perfidious Albion; had an absolutely miserable, pitiful first year; but then Andrea came to work and study here also, and pretty much everything good that has happened ever since I have her to thank for. There's no way on earth I could have done any of this without you, science and life. Hopefully if my examiners like this thesis and I get \sout{ordained} a PhD in Biology you'll stop saying that I'm not a real biologist? If so, this thesis, which is already partly yours, is dedicated to you.
